On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-10-12 paper.tex
Written down final implication of 4.1

\subsection{Formalism of Tulenbaev factorization theorem}
%{\it Tulenbaev's cube} is a collection of abstract groups and morphisms between them which make the diagram below commute.
Suppose we are given a commutative diagram of groups
\[\xymatrix{
G_{123} \ar[rr]_{f_{23}} \ar[dd]_{f_{12}} \ar[rd]_{f_{13}} &                        & G_{23} \ar[dd]^(.3){g_2^3} \ar[rd]^{g^2_3} &           \\
                                & G_{13} \ar[rr]^(.3){g^1_3} \ar^(.3){g^3_1}[dd] &                   & G_3 \ar[dd]_{h_3} \\
G_{12} \ar[rr]^(.3){g_2^1} \ar[rd]_{g_1^2}          &                        & G_2 \ar[rd]_{h_2}         &           \\
                                & G_1 \ar[rr]_{h_1}              &                   & G}\]
such that $g_1^3$ is a precrossed module, $h_3$ is a crossed module and, moreover, that $(g_3^1, h_1) \colon g_1^3 \to h_3$ is a map of precrossed modules.
\begin{comment}In addition, we require these maps to satisfy the following list of axioms:
\begin{enumerate}
 \item $G_1$ acts on $G_{13}$, $G$ acts on $G_3$ %??? vertical arrows $G_{13} \to G_1$ and $G_3 \to G$ are crossed modules
 \item for every $b \in G_{13}$ and $x \in G_1$ one has $g_1^3(b ^ x) = x^{-1} \cdot g_1^3(b) \cdot x$; (precrossed)
 \item for every $x\in G_{13}$, $b \in G_{13}$ one has $g_3^1(b^x) = g_3^1(b)^{h_1(x)}$; ($g_3^1$ map of precrossed modules?)
 \item for every $z_1, z_2 \in G_3$ one has $z_1^{-1} z_2 z_1 = z_2^{h_3(z_1)}$ (Peiffer)
\end{enumerate}
\end{comment}
%\end{dfn}

Now set $V = G_1 \times G_2 \times G_3$, $W = G_{12} \times G_{13} \times G_{23}$.
We define an operation $\star \colon W \times V \to V$ as follows. For $v = (x, y, z) \in V$ and $(a, b, c) \in W$ we set 
\[(a, b, c) \star (x, y, z) = (x \cdot g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot y \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z).\]

\begin{lemma} For every $v \in V$ one has 
 \begin{equation*}(a', b', c') \star \left( (a, b, c) \star v \right) = (a \cdot a', b \cdot {b'}^{g_1^2(a)^{-1}}, c \cdot c') \star v.\end{equation*}
\end{lemma}
\begin{proof}
Set $v'=(x', y', z') = (a, b, c) \star v$ and $(x'', y'', z'') = (a', b', c') \star v'$.
Since $g_1^3$ is a precrossed module we immediately obtain:
\begin{align*} 
 x'' =& x' \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b) \cdot g_1^2(a) \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b \cdot b'^{g_1^2(a')^{-1}}) g_1^2(a \cdot a'),\\
 y'' =& g_2^1(a')^{-1} \cdot g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \cdot g_2^3(c') = g_2^1(aa')^{-1} \cdot y \cdot g_2^3(cc'). \end{align*}

@@

Now we define a relation on the set $V$.
By definition, two elements $v$, $v'$ are declared congruent (denoted $v \sim v'$)
 if $v' = w \star v$ for some triple $(a, b, c) \in W$. In view of thea above lemma this relation is an equivalence relation
 and we denote the quotient set of $V$ modulo this relation by $V'$.

\begin{lemma}
 Then the kernel of $h_3\colon G_3\to G_1$ is generated by $g_3^1(\Ker(g_1^3))$.
\end{lemma}

>>>>

\subsection{Formalism of Tulenbaev factorization theorem}
Suppose we are given a cube-like commutative diagram of groups
\begin{equation} \label{eq:cube} \begin{split} \xymatrix{
G_{123} \ar[rr]_{f_{23}} \ar[dd]_{f_{12}} \ar[rd]_{f_{13}} &                        & G_{23} \ar@{-->}[dd]^(.3){g_2^3} \ar[rd]^{g^2_3} &           \\
                                & G_{13} \ar[rr]^(.3){g^1_3} \ar^(.3){g^3_1}[dd] &                   & G_3 \ar[dd]_{h_3} \\
G_{12} \ar@{-->}[rr]^(.3){g_2^1} \ar[rd]_{g_1^2}          &                        & G_2 \ar@{-->}[rd]_{h_2}         &           \\
                                & G_1 \ar[rr]_{h_1}              &                   & G} \end{split} \end{equation}
such that $g_1^3$ is a precrossed module, $h_3$ is a crossed module and, moreover, that $(g_3^1, h_1) \colon g_1^3 \to h_3$ is a map of precrossed modules.

Set $V = G_1 \times G_2 \times G_3$, $W = G_{12} \times G_{13} \times G_{23}$.
We define an operation $\star \colon W \times V \to V$ as follows. For $v = (x, y, z) \in V$ and $(a, b, c) \in W$ we set 
\[(a, b, c) \star (x, y, z) = (x \cdot g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot y \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z).\]

\begin{lemma} For every $v \in V$ one has 
 \begin{equation*}(a', b', c') \star \left( (a, b, c) \star v \right) = (a \cdot a', b \cdot {b'}^{g_1^2(a)^{-1}}, c \cdot c') \star v.\end{equation*}
\end{lemma}
\begin{proof}
Set $v'=(x', y', z') = (a, b, c) \star v$ and $(x'', y'', z'') = (a', b', c') \star v'$.
Since $g_1^3$ is a precrossed module we immediately obtain:
\begin{align*} 
 x'' =& x' \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b) \cdot g_1^2(a) \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b \cdot b'^{g_1^2(a)^{-1}}) g_1^2(a \cdot a'),\\
 y'' =& g_2^1(a')^{-1} \cdot g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \cdot g_2^3(c') = g_2^1(aa')^{-1} \cdot y \cdot g_2^3(cc'). \end{align*}

@@

The above lemma allows us to define an equivalence relation on the set $V$ as follows.
By definition, two elements $v, v' \in V$ are congruent (denoted $v \sim v'$)
 if $v' = w \star v$ for some triple $(a, b, c) \in W$.

\begin{lemma} Suppose that the back face $(f_{12}, f_{23}, g_2^1, g_2^3)$ of~\eqref{eq:cube} is pullback.
If for some $z\in G_3$ holds $(1, 1, 1)\sim (1, 1, z)$ then $z \in g_3^1(\Ker(g_1^3)).$ \end{lemma}
\begin{proof} By assumption, there exists $(a, b, c)\in W$ such that
 \[ (a, b, c) \star (1, 1, 1) = ( g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-1}) = (1,1,z). \]
 By assumption there exists $e \in G_{123}$ such that $f_{12}(e) = a$, $f_{23}(e) = c$, hence
 \[ 1 = g_1^3(b) \cdot g_1^2(f_{12}(e)) = g_1^3(b \cdot f_{13}(e)),\ z = g_3^2(f_{23}(e))^{-1} \cdot g_3^1(b) = g_3^1(b \cdot f_{13}(e))^{-1}. \qedhere\] \end{proof}
